\section{Deployment}\label{sec:deployment}

\subsection{Overview}\label{subsec:overview}
The application is containerized using Docker, which simplifies deployment and ensures consistency across different environments.
This section outlines the Docker-related files and configurations used.

\subsection{Dockerfiles}\label{subsec:dockerfiles}
The architecture utilizes Dockerfiles for both the frontend and backend components:

\begin{itemize}
    \item \textbf{Backend Dockerfile:}
    The Dockerfile starts with a base image of golang:1.22, copies the application code, and compiles it.
    The binary is then packaged into a minimal Alpine image.
    This two-stage build process ensures the final image is lightweight and secure.

    \item \textbf{Frontend Dockerfile:}
    The frontend is built using the Angular framework.
    The Dockerfile uses node:18 as a base to install dependencies and build the static files.
    These files are then served using nginx in a subsequent stage, similar to the backend, to keep the image minimal.
\end{itemize}

\subsection{Deployment Strategy}\label{subsec:deployment-strategy}
The deployment utilizes GitHub Actions for CI/CD, automatically building Docker images and pushing them to GitHub Container Registry.
From there, the images can be pulled directly and executed on any environment with Docker installed.
The images can be found at the following location:

\begin{itemize}
    \item \url{https://github.com/HardCodedCoder/Typecode-Registry/pkgs/container/typecode-registry}
    \item \url{https://github.com/HardCodedCoder/Typecode-Registry/pkgs/container/typecode-registry-backend}
\end{itemize}
